---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

Read activity.csv hat had been extract at local directory file is downloaded

```{r}
read_df <- read.csv("activity.csv", header = T, sep = ",")
```


set date format 

```{r}
read_df$date <- as.Date(read_df$date, format = "%Y-%m-%d")
```


## What is mean total number of steps taken per day?


Agregate by total steps and day with naming column 'Steps' and 'Date'

```{r}
#act.day <- aggregate(read_df$steps, by = list(read_df$date), sum )
act.day <- aggregate(steps ~ date, read_df, sum)
head(act.day)
names(act.day)[2] <- "Steps"
names(act.day)[1] <- "Date"
head(act.day)
```

Histogram total number of step per day

```{r}
hist(act.day$Steps, col = 2, main = "Histogram number of steps taken each day", xlab = "Total number of steps taken each day")
```


Calculate mean and median of the total number of steps taken per day

```{r}
mean(act.day$Steps)
median(act.day$Steps)
```







## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
